Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git]

### 2022-03-19 outputs/paper/paper.Rmd
ggplot

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
```
The data comes from US General Social Survey.
1.Conveying a sense of the dataset of interest.
2.Dicussion of the survey's methodology and its key features, strengths, weaknesses.
For instance what is the population, frame and sample.
How is the sample recruited 
what sampling approach is taken
what are some of the trade offs of this 
how is non response handled.
(What is good and bad about it

@@

@@

reduced_data %>%
  drop_na(nation_race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Opinion on National Spending on Improving Conditions of Black Population",
       caption = "Figure 3: Distribution of survey respondents' Race") +
  facet_wrap(~ pres16)

>>>>

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
```
* number of survey participants of age in the range of 20~40 is unexpectedly low -> not many people in ages between 20-40 participated in the survey
* Clinton's vote is higher than trump's vote in this survey, which contradicts the election result of 2016, reader should keep in mind that this survey is more biased towards clinton.

1.Conveying a sense of the dataset of interest.
2.Dicussion of the survey's methodology and its key features, strengths, weaknesses.
For instance what is the population, frame and sample.
How is the sample recruited 
what sampling approach is taken
what are some of the trade offs of this 
how is non response handled.
(What is good and bad about it

@@

reduced_data %>%
  ggplot(aes(x = pres16, fill = pres16)) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's vote choice of 2016 Presidential election",
       caption = "Figure 3: Distribution of survey respondents' vote choice") +
  theme(legend.position = "none")

@@

reduced_data %>%
  drop_na(nation_race) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Opinion on National Spending on Improving Conditions of Black Population",
       caption = "Figure 4: Distribution of survey respondents' Race") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())
